Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

From a qualitative point of view, these results show consensus in a few key aspects:
\begin{itemize}
 \item Teaching staff want to have support from their institutions. This
   is probably due to the strict European data regulations on data protection,
   but also to avoid the overhead required to sign up new students every year.
   In general, additional support with specific formation and access to IT help desk for specific features
   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
   surveys: they prefer whatever ``messaging'' application provided by
  as well as the fact that this application is the ``official'' for the university, as shown in
   Table \ref{tab:interaction}.
 \item Teachers need sustainability. The main reason is that implementing
   changes is expensive in terms of effort and prone to errors in the first
   years. Therefore, it is logical that if
   chatbots or messaging platforms are to be introduced, teachers want this change
   to be as permanent as possible.
 \item Keep it Simple. Media interaction requirements are simple and only 2.4\% of teachers are requesting more features. This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
\end{itemize}

@@

% Only some COVID-response relationship.
In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies. The reason being that it does not
bring major changes in attitude 
%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}), 
%or simply the introduction of new degrees. 
Although changes driven by external forces do offer the chance of piloting new technologies, they do not
seem to bring internal changes in teachers' attitudes (which, after all, is
bound to be the same). In absence of a clear answer in this direction, the right
moment to introduce new technologies is always when the IT and managing staff is
ready to support it (since, as we have seen before, "official" support is one of
the factors that is most valued by teachers).

>>>>

From a qualitative point of view, these results show consensus in a few key aspects:
\begin{itemize}
 \item Teaching staff want to have support from their institutions. This
   is probably due to the strict European data regulations on data protection,
   but also to avoid the overhead required to sign up new students every year.
   In general, additional support with specific formation and access to IT help desk for specific features
   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
   surveys: they prefer whatever ``messaging'' application provided by
  as well as the fact that this application is the ``official'' for the university, as shown in
   Table \ref{tab:interaction}.
 \item Teachers need sustainability. The main reason is that implementing
   changes is expensive in terms of effort and prone to errors in the first
   years. Therefore, it is logical that if
   chatbots or messaging platforms are to be introduced, teachers want this change
   to be as permanent as possible.
 \item Keep it Simple. Media interaction requirements are simple and only 2.4\% of educators are requesting more features. This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
\end{itemize}

@@

% Only some COVID-response relationship.
In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies. The reason being that it does not
bring major changes in attitude 
%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}), 
%or simply the introduction of new degrees. 
Although changes driven by external forces do offer the chance of piloting new technologies, they do not
seem to bring internal changes in educators' attitudes (which, after all, is
bound to be the same). In absence of a clear answer in this direction, the right
moment to introduce new technologies is always when the IT and managing staff is
ready to support it (since, as we have seen before, "official" support is one of
the factors that is most valued by teachers).
